Evidence for a Third Color Parameter Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2018-05-17 submit/fix.tex
address a referee comment on measuring one but not another feature

\added{
\begin{equation}
\begin{pmatrix}
\small
\begin{array}{rrrrrrr}
EW_{\mathrm{Ca}} & 7.0  \pm 0.5 \times 10^{ 2} & 6.7  \pm 0.3 \times 10^{ 2} & 3.7  \pm 1.1 \times 10^{ 2} & 3.3  \pm 6.2 \times 10^{ 1} & 7.7  \pm 17.0 \times 10^{ 0} & 6.3  \pm 11.2 \times 10^{ 1} \\
5.0  \pm 0.2 \times 10^{ 1} & EW_{\mathrm{Si}} & 4.9  \pm 0.2 \times 10^{ 1} & 2.5  \pm 0.2 \times 10^{ 0} & 4.7  \pm 3.3 \times 10^{ 0} & 1.2  \pm 1.5 \times 10^{ 0} & 1.1  \pm 1.2 \times 10^{ 1} \\
3.8  \pm 0.2 \times 10^{ 2} & 3.9  \pm 0.2 \times 10^{ 2} & \lambda_{\mathrm{Si}} & 1.4  \pm 0.3 \times 10^{ 2} & 7.4  \pm 8.8 \times 10^{ 1} & 4.3  \pm 6.8 \times 10^{ 1} & 4.5  \pm 7.0 \times 10^{ 1} \\
9.9  \pm 0.4 \times 10^{-1} & 2.9  \pm 0.2 \times 10^{-1} & 9.7  \pm 0.4 \times 10^{-1} & x_1 & 5.2  \pm 1.4 \times 10^{-1} & 2.3  \pm 1.6 \times 10^{-1} & 6.7  \pm 2.3 \times 10^{-1} \\
5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} & E_{\gamma^0}({\hat{B}}-{\hat{V}})& 5.4  \pm 0.5 \times 10^{-3} & 5.4  \pm 0.5 \times 10^{-3} \\
1.5  \pm 0.3 \times 10^{-3} & 1.4  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} & 1.5  \pm 0.3 \times 10^{-3} &  E_{\gamma^1}({\hat{B}}-{\hat{V}}) & 1.5  \pm 0.3 \times 10^{-3} \\
2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & 2.6  \pm 1.1 \times 10^{-3} & A_{p,V} \\
\end{array}
\end{pmatrix}.
\label{ellipse:eqn}
\end{equation}
}

>>>>

\added{
The correlation matrix in Eq.~\ref{corr:eqn} is not close to being singular, meaning that the each of the features conveys
independent supernova variability.  Nevertheless, a strong correlation between two features means that the determination
of one would reduce the residual dispersion in the other.  This information is conveyed in the matrix
\begin{equation}
M =
\begin{pmatrix}
\tiny
\begin{array}{rrrrrrr}
2.76  \pm 0.06 \times 10^{ 1} & 2.75  \pm 0.06 \times 10^{ 1} & 2.67  \pm 0.06 \times 10^{ 1} & 2.75  \pm 0.05 \times 10^{ 1} & 2.74  \pm 0.06 \times 10^{ 1} & 2.71  \pm 0.06 \times 10^{ 1} & 2.75  \pm 0.06 \times 10^{ 1} \\
7.04  \pm 0.16 \times 10^{ 0} & 7.08  \pm 0.16 \times 10^{ 0} & 7.02  \pm 0.16 \times 10^{ 0} & 3.86  \pm 0.19 \times 10^{ 0} & 7.01  \pm 0.16 \times 10^{ 0} & 6.79  \pm 0.21 \times 10^{ 0} & 7.06  \pm 0.16 \times 10^{ 0} \\
1.98  \pm 0.04 \times 10^{ 1} & 2.03  \pm 0.05 \times 10^{ 1} & 2.05  \pm 0.05 \times 10^{ 1} & 2.03  \pm 0.05 \times 10^{ 1} & 2.04  \pm 0.05 \times 10^{ 1} & 2.04  \pm 0.05 \times 10^{ 1} & 2.04  \pm 0.05 \times 10^{ 1} \\
9.92  \pm 0.18 \times 10^{-1} & 5.43  \pm 0.23 \times 10^{-1} & 9.86  \pm 0.19 \times 10^{-1} & 9.95  \pm 0.18 \times 10^{-1} & 9.86  \pm 0.19 \times 10^{-1} & 9.71  \pm 0.26 \times 10^{-1} & 9.92  \pm 0.19 \times 10^{-1} \\
7.33  \pm 0.31 \times 10^{-2} & 7.32  \pm 0.32 \times 10^{-2} & 7.37  \pm 0.32 \times 10^{-2} & 7.32  \pm 0.32 \times 10^{-2} & 7.38  \pm 0.32 \times 10^{-2} & 7.36  \pm 0.33 \times 10^{-2} & 7.36  \pm 0.32 \times 10^{-2} \\
3.82  \pm 0.42 \times 10^{-2} & 3.73  \pm 0.41 \times 10^{-2} & 3.88  \pm 0.43 \times 10^{-2} & 3.79  \pm 0.42 \times 10^{-2} & 3.88  \pm 0.44 \times 10^{-2} & 3.89  \pm 0.44 \times 10^{-2} & 3.88  \pm 0.44 \times 10^{-2} \\
4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.95  \pm 1.09 \times 10^{-2} & 4.97  \pm 1.10 \times 10^{-2} 
\\\end{array}
\end{pmatrix}.
\label{ellipse:eqn}
\end{equation}
For indeces $i, j \in \{EW_{\mathrm{Ca}}, EW_{\mathrm{Si}}, \lambda_{\mathrm{Si}}, x_1, E_{\gamma^0}({\hat{B}}-{\hat{V}}), E_{\gamma^1}({\hat{B}}-{\hat{V}}), A_{p,V}\}$, $M_{ii}$ is the standard deviation in the distribution of parameter $i$, and for $i \ne j$ $M_{ij}$ is the standard deviation in parameter $i$
if parameter $j$ were known perfectly.  For example, for $i= EW_{\mathrm{Si}}$ the standard deviation is 7.08 but when $j=x_1$
is fixed its
standard deviation drops to 3.86.  Therefore, an analysis that considers $x_1$ but not $EW_{\mathrm{Si}}$ would not account for
$3.86\vec{\beta}=\{0.14 ,  0.09,  0.08,  0.07,  0.04 \}$ ${\hat{U}}{\hat{B}}{\hat{V}}{\hat{R}}{\hat{I}}$ magnitude dispersions
that are not intrinsically random.
}
